\documentclass{scrartcl}

%This CV template is based on the DFG-form 53.200 – 07/25
% https://www.dfg.de/de/formulare-53-200-elan-246806
% 
%Author: Oliver Wallscheid, oliver.wallscheid@uni-siegen.de
% 

\usepackage[utf8]{inputenc}
\usepackage[english]{proposal}

\setboolean{finalcompile}{true}

% show DFG template version the current LaTeX template is based on in the header. Will be deactivated when 'finalcompile' is set 'true'
\ihead*{DFG-form 53.200 - 07/25}

\input{Header.tex}

\linespread{1.2}
\setlength{\parskip}{0.3em}

\tikzset{notestyleraw/.append style={align= justify}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%%%  CV DFG Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\begin{document}

\section*{Curriculum Vitae}

\subsection*{Personal Data}
    
\begin{longtable}{|p{0.3\textwidth-2\tabcolsep}|p{0.7\textwidth-2\tabcolsep}|}
    \hline
    Title & Dr. \\
    \hline
    First name & Chung-Wen \\
    \hline
    Name & Lin \\
    \hline
    Current position & Postdoctoral Researcher \\
    \hline
    Current institution(s)/site(s), country & Helmholtz Munich, Institute of Network Biology, Germany \\
    \hline
    Identifiers/ORCID &  \\
    \hline
\end{longtable}

\subsection*{Qualifications and Career}

\begin{longtable}{|p{0.35\textwidth-2\tabcolsep}|p{0.65\textwidth-2\tabcolsep}|}
    \hline
    \textbf{Stages} & \textbf{Periods and Details}\\
    \hline
    Degree programme & Ph.D. in Life Sciences, National Cheng Kung University, Taiwan (07/2012 -- 09/2017) \newline
    M.S. in Life Sciences, National Cheng Kung University, Taiwan (09/2003 -- 06/2005)\\
    \hline
    Doctorate  & 09/2017, National Cheng Kung University, Taiwan. \newline Supervisor: Prof. Hao-Jen Huang \newline Thesis: "Transcriptome analysis provide insights into environmental stresses in plants" \\
    \hline
    Stages of academic/professional career & \textbf{01/2018 -- Present: Postdoctoral Researcher} \newline
    Institute of Network Biology, Helmholtz Munich, Germany. \newline
    Research: Mapping SARS-CoV-2 viral-human protein interaction networks; Arabidopsis drought stress proteomics/transcriptomics. \\
    \vspace{0.2cm}
    \textbf{05/2016 -- 06/2016: Visiting Scholar} \newline
    National Institute for Basic Biology, Japan. \newline
    Research: Gene co-expression network clustering in plant systems. \\
    \vspace{0.2cm}
    \textbf{07/2010 -- 06/2012: R&D Engineer} \newline
    ProMD Biotech Co., Ltd., Taiwan. \newline
    Research: Probiotics identification and functional assays. \\
    \vspace{0.2cm}
    \textbf{08/2007 -- 02/2010: Research Assistant} \newline
    Academia Sinica, Taiwan. \newline
    Research: Nutrient deficiency effects in Arabidopsis and cucumber using microarrays. \\
    \hline
\end{longtable}

\subsection*{Supplementary Career Information}
2 children, born 05/2022 and 11/2024.

\subsection*{Activities in the Research System}
Reviewer for bioinformatics and plant science journals.

\subsection*{Supervision of Researchers in Early Career Phases}
Supervised graduate students and led practical teaching sessions at Helmholtz Munich and National Cheng Kung University.

\section*{Scientific Results}

\subsection*{Category A}
\begin{enumerate}
    \item \textbf{Kim, D.K., Weller, B., Lin, C.W., Sheykhkarimli, D., Knapp, J.J., et al.} (2022). A proteome-scale map of the SARS-CoV-2-human contactome. \textit{Nature Biotechnology}. (co-first author)
    \item \textbf{Weller, B., Lin, C.W., Pogoutse, O., Sauer, M., de la Rosa, N., Strobel, A., et al.} (2023). A resource of human coronavirus protein-coding sequences in a flexible, multipurpose Gateway Entry clone collection. \textit{G3: Genes, Genomes, Genetics}.
    \item \textbf{de la Rosa, N.M., Lin, C.W., Kang, Y.J., Dhondt, S., Gonzalez, N., Inzé, D., et al.} (2019). Drought resistance is mediated by divergent strategies in closely related Brassicaceae. \textit{New Phytologist}, 223(2), 783–797. (co-first author)
    \item \textbf{Lin, C.W., Fu, S.F., Liu, Y.J., Chen, C.C., Chang, C.H., Yang, Y.W., et al.} (2019). Analysis of ambient temperature-responsive transcriptome in shoot apical meristem of heat-tolerant and heat-sensitive broccoli inbred lines during floral head formation. \textit{BMC Plant Biology}, 19(1), 3.
    \item \textbf{Lin, C.W., Huang, L.Y., Huang, C.L., Wang, Y.C., Lai, P.H., Wang, H.V., et al.} (2017). Common Stress Transcriptome Analysis Reveals Functional and Genomic Architecture Differences Between Early and Delayed Response Genes. \textit{Plant and Cell Physiology}, 58(3), 546–559. (co-first author)
\end{enumerate}

\subsection*{Category B}
None.

\subsection*{Academic Distinctions}
None.

\section*{Other Information}
None.

\end{document}