\section{Requested modules/funds}

\subsection{Basic Module}

\subsubsection{Funding for Staff}
We request funding for one doctoral researcher (PhD Student, TV-L 13, 65\%) for 36 months. 

\begin{tabular}{lr}
\textbf{Item} & \textbf{Amount (\euro)} \\
\hline
Doctoral Researcher (TV-L 13, 65\%), 36 months & 152\,100 \\
\hline
\end{tabular}

\subsubsection{Direct Project Costs}

\subsubsubsection{Equipment up to 10\,000\,\euro, Software and Consumables}
None.

\subsubsubsection{Travel Expenses}
We apply for a total of \textbf{10\,000\,\euro} for travel expenses.

\subsubsubsection{Visiting Researchers}
None.

\subsubsubsection{Expenses for Laboratory Animals}
None.

\subsubsubsection{Other Costs}
We request funds for commercial Large Language Model (LLM) API services and subscriptions.

\begin{tabular}{lr}
\textbf{Item} & \textbf{Amount (\euro)} \\
\hline
LLM API Services (Claude, OpenAI) for Benchmarking & 10\,800 \\
\hline
\end{tabular}

\textit{Justification:} While the primary inference will be performed locally on the Mac Studio, access to state-of-the-art commercial models (e.g., Anthropic Claude, GPT-4o) is essential for (1) establishing a "gold standard" reasoning baseline to evaluate our local distilled models, (2) accelerating code development for the web platform, and (3) accessing specialized knowledge bases not yet available in open weights. The estimated cost is based on a monthly usage of approx. 300\,\euro\ for 36 months.

\subsubsubsection{Project-related publication expenses}
We apply for a total of \textbf{1\,500\,\euro} for publication expenses.

\subsubsection{Instrumentation}

\subsubsubsection{Equipment exceeding 10\,000\,\euro}
\textbf{High-Performance Node (512GB RAM):} 15\,000\,\euro.

\subsubsubsection{Major Instrumentation exceeding 50\,000\,\euro}
None.

\subsection{Module Temporary Position for Principal Investigator}
We request a full-time position for the Principal Investigator (Eigene Stelle) for 36 months. 

\begin{tabular}{lr}
\textbf{Item} & \textbf{Amount (\euro)} \\
\hline
Principal Investigator (TV-L 13/14, 100\%), 36 months & 252\,000 \\
\hline
\end{tabular}