\section{Innovation and Impact}

\subsection{Methodological Innovations}
\begin{enumerate}
    \item \textbf{LLM-Based Biological Reasoning Framework:} Novel application of large language models as biological reasoning engines, enabling integration of multi-modal evidence (expression, abundance, localization, function) that purely numerical approaches cannot achieve.
    \item \textbf{Three-Score Assessment System:} A new framework combining likelihood, confidence, and concordance scores that provides nuanced, probabilistic assessments rather than binary predictions.
    \item \textbf{Hybrid Neuro-Symbolic Architecture:} Integration of LLM semantic reasoning with GNN topological learning, capturing complementary biological signals as demonstrated by our preliminary results (4.3-fold improvement in pathway validation).
    \item \textbf{Knowledge Distillation Pipeline:} Application of teacher-student model architectures to biological prediction, creating efficient, deployable models that preserve the reasoning capabilities of larger systems.
\end{enumerate}

\subsection{Scientific Impact}
\begin{itemize}
    \item \textbf{Disease Research:} Tissue-specific pathway analysis for complex diseases with tissue-selective manifestation.
    \item \textbf{Drug Discovery:} Context-aware therapeutic target identification, enabling reduced off-target effects through tissue-specific network analysis.
    \item \textbf{Biomarker Development:} Tissue-specific interaction signatures as candidates for diagnostic applications.
    \item \textbf{Community Resource:} A publicly accessible, continuously updated interactome database for the systems biology community.
\end{itemize}

